Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-08-02 manuscript/appendix.Rmd
reknit appendix

\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S2: Correlations among latitude and climate variables", out.height='95%', fig.pos='H'}

>>>>

\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S2: Scatterplots and Pearson's R values for relationships between latitude and climate variables", out.height='95%', fig.pos='H'}
